Four Problems for Sophistication

### 2015-01-08 Facticity/Facticity/paper.tex
abstract

In this paper we describe four fundamental problems that arise with all existing proposals, showing each of them to be \emph{unsound}. Based on these results we we lay down the view that this unsoundness is fundamental: while it is certainly possible to make nontrivial and useful statements about the structural properties of binary strings, it is \emph{not} possible to objectively quantify its amount of meaningful information.
\end{abstract}

>>>>

In this paper we describe four fundamental problems that arise with all existing proposals, showing each of them to be \emph{unsound}. Based on these results we we lay down the view that this unsoundness is fundamental: while many nontrivial and useful structural properties of binary strings can be detected without a priori assumptions, it is \emph{not} possible to objectively quantify its sophistication.
\end{abstract}
